\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-16 canonicitymodel.tex
Fixing biblography.

Canonicity is one of the basic criteria to consider a dependent type theory to be ``a programming language or as a computational foundation for mathematics''\footnote{See nlab explanation: \href{https://ncatlab.org/nlab/show/canonical+form}{Canonical Form}}.
We can even argue that, if this theorem is proven in a constructive meta-logic\footnote{QIIT does have computational content\citep{altenkirch2016type}}, 
then by Curry-Howard Correspondence, this theorem provides a big-step interpreter for closed term of boolean type.

>>>>

Canonicity is one of the basic criteria to consider a dependent type theory to be ``a programming language or as a computational foundation for mathematics''\footnote{See nlab explanation: \href{https://ncatlab.org/nlab/show/canonical+form}{Canonical Form}}.
We can even argue that, if this theorem is proven in a constructive meta-logic\footnote{QIIT does have computational content\citep{altkap2016}}, 
then by Curry-Howard Correspondence, this theorem provides a big-step interpreter for closed term of boolean type.

### 2022-06-16 coq-example.tex
Fixing biblography.

\subsection{Abstract Interpreters for Imp}
The second example is adapted and modified from the Familia\citep{zhang2017familia}
-- contrary to our first example, we use big-step interpreter and fuel to indicate the operational semantic on an imperative language with side-effect, and we specify the abstract interpretation and prove its soundness, with some of postulation on both computation and property. Then we extend the language feature and we instantiate the postulation on computation for both concrete interpreters and abstract interpreters. Thanks to the compilation, we can directly run the resulting abstract interpreters.

>>>>

\subsection{Abstract Interpreters for Imp}
The second example is adapted and modified from the Familia\citep{zm2017}
-- contrary to our first example, we use big-step interpreter and fuel to indicate the operational semantic on an imperative language with side-effect, and we specify the abstract interpretation and prove its soundness, with some of postulation on both computation and property. Then we extend the language feature and we instantiate the postulation on computation for both concrete interpreters and abstract interpreters. Thanks to the compilation, we can directly run the resulting abstract interpreters.

### 2022-06-16 standardmodel.tex
Fixing biblography.

Once we have the syntax of our theory, the first question is if our theory is consistent, i.e., if we can syntactically derive bottom in our theory. We prove the consistency by extending the standard model from \citep{altenkirch2016type,kaposi2017type, kaposi2019gluing} and their formalization, where they formally resort to the concept of \textit{algebra} of QIIT, here we only consider inductively interpreting each syntax piece into naive set theory that is also respecting judgemental equalities\footnote{In our appendix, we still interpret into Agda component to be more precise and less error-prone, also we need the inductive facility from Agda.} The main idea of the proof is that: 1. we use $\denotesS{}$ to map each intrinsic well-typed syntax piece into a mathematical object; 2. we define proof-irrelevant proposition $\models_S$ for each syntactical $\vdash$, and derive compatibility lemma. We will mainly focus on the definition of $\denotesS{}$ and omit the verification of $\models_S$\footnote{Actually our 1 is acting exactly as an interpretation function, and in our agda formulation we only do 1 because 2 is automatic; here we make 2 explicit to make our formulation more accessible and uniform}, and also we omit the verification of equality (i.e. the judgementally-equal syntax needs to be mapped to the same data for well-defined-ness).

>>>>

Once we have the syntax of our theory, the first question is if our theory is consistent, i.e., if we can syntactically derive bottom in our theory. We prove the consistency by extending the standard model from \citep{altkap2016,kaposi2017type, kaposi2019gluing} and their formalization, where they formally resort to the concept of \textit{algebra} of QIIT, here we only consider inductively interpreting each syntax piece into naive set theory that is also respecting judgemental equalities\footnote{In our appendix, we still interpret into Agda component to be more precise and less error-prone, also we need the inductive facility from Agda.} The main idea of the proof is that: 1. we use $\denotesS{}$ to map each intrinsic well-typed syntax piece into a mathematical object; 2. we define proof-irrelevant proposition $\models_S$ for each syntactical $\vdash$, and derive compatibility lemma. We will mainly focus on the definition of $\denotesS{}$ and omit the verification of $\models_S$\footnote{Actually our 1 is acting exactly as an interpretation function, and in our agda formulation we only do 1 because 2 is automatic; here we make 2 explicit to make our formulation more accessible and uniform}, and also we omit the verification of equality (i.e. the judgementally-equal syntax needs to be mapped to the same data for well-defined-ness).
